The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2017-03-08 manuscript/manuscript.Rnw
fix } typo in reference

Previous studies of some species (i.e., \human, \mouse, \cow, and
\elephant) have provided some preliminary answers to these questions.
They revealed a stunning divergence in the genetics of the placenta,
especially in later stages of pregnancy
\cite{Carter2012:Evolutionofplacentalfunction,Knox.ea2008:Genomicevolutionofplacenta,Su.ea2002:Large-scaleanalysisofhuman,Hou.ea2012:Elephanttranscriptomeprovidesinsights}}.
For example, each superorder (Euarchontoglires, Laurasiatheria,
Afrotheria, and Xenartha, \cref{fig:species_tree})
has evolved expansive placenta-specific gene
families with expression patterns that can vary in space and time
\cite{Green.ea2000:Pregnancy-associatedbovineandovine}. These include
independent expansions of the prolactins in \mouse, \carmeli, \galili,
and \cow, \acp{PSG} in \human and \mouse, \acp{PAG} in \cow, genes
related to the thymus-specific serine protease \ac{PRSS16} in
\elephant, and the expansion of the growth hormone and
chorionic gonadotropin beta genes in anthropoid primates
\cite{Haig2008:Placentalgrowthhormone-relatedproteins,Rawn.ea2008:evolutionregulationandfunction}.
Expression patterns of specific genes also can vary widely between
species. For example, the expression of orthologous genes in the
placenta have been found to vary substantially between \human and
\mouse \cite{Su.ea2002:Large-scaleanalysisofhuman}.

>>>>

Previous studies of some species (i.e., \human, \mouse, \cow, and
\elephant) have provided some preliminary answers to these questions.
They revealed a stunning divergence in the genetics of the placenta,
especially in later stages of pregnancy
\cite{Carter2012:Evolutionofplacentalfunction,Knox.ea2008:Genomicevolutionofplacenta,Su.ea2002:Large-scaleanalysisofhuman,Hou.ea2012:Elephanttranscriptomeprovidesinsights}.
For example, each superorder (Euarchontoglires, Laurasiatheria,
Afrotheria, and Xenartha, \cref{fig:species_tree})
has evolved expansive placenta-specific gene
families with expression patterns that can vary in space and time
\cite{Green.ea2000:Pregnancy-associatedbovineandovine}. These include
independent expansions of the prolactins in \mouse, \carmeli, \galili,
and \cow, \acp{PSG} in \human and \mouse, \acp{PAG} in \cow, genes
related to the thymus-specific serine protease \ac{PRSS16} in
\elephant, and the expansion of the growth hormone and
chorionic gonadotropin beta genes in anthropoid primates
\cite{Haig2008:Placentalgrowthhormone-relatedproteins,Rawn.ea2008:evolutionregulationandfunction}.
Expression patterns of specific genes also can vary widely between
species. For example, the expression of orthologous genes in the
placenta have been found to vary substantially between \human and
\mouse \cite{Su.ea2002:Large-scaleanalysisofhuman}.
